An Approach to Off-line Handwriting Recognition through Segmentation Techniques and Deep Neural Networks

### 2017-12-17 Report/paper.tex
change sizes of images

\begin{figure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/bad_char1}
\end{subfigure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[width=\linewidth]{images/bad_char2}
\end{subfigure}
\caption{Examples of written 'z' characters, which are hard to recognise or ambiguous.}
\label{fig:char}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}{\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{images/vpp}
    \vspace{-5px}
    \caption*{Vertical projection profile.}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{images/rules}
    \vspace{-5px}
    \caption*{Rule based correction.}
    \end{subfigure}
    \begin{subfigure}{\linewidth}
    \centering
    \includegraphics[width=.7\linewidth]{images/nn}
    \vspace{-5px}
    \caption*{Correction through neural network.}
    \end{subfigure}
    \caption{Word segmentation steps}
    \label{fig:char_segm}
\end{figure}

@@

        \Tree [.{(T, 0.1)}
        [.{(Te , 0.08)} {(Tes, 0.048)} {(Te5 , 0.032)} ]
        [.{(Tl , 0.02)} {(Tls, 0.012)} {(Tl5 , 0.008)} ]
\caption{A list of the trees for the word 'Yes' with branching factor 2. The characters have the following probabilities: $P(Y)=0.9, P(T)=0.1, P(e)=0.8, P(l)=0.2, P(s)=0.6, P(5)=0.4$. Other characters have probabilities which are neglible.}

>>>>

\begin{figure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[height=2cm]{images/bad_char1}
\end{subfigure}
\begin{subfigure}{.23\textwidth}
  \centering
  \includegraphics[height=2cm]{images/bad_char2}
\end{subfigure}
\caption{Examples of written 'z' characters, which are hard to recognise or are ambiguous.}
\label{fig:char}
\end{figure}

@@

\begin{figure*}
    \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/vpp}
    \caption*{Vertical projection profile.}
    \end{subfigure}
    \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/rules}
    \caption*{Rule based correction.}
    \end{subfigure}
    \begin{subfigure}{0.33\textwidth}
    \centering
    \includegraphics[width=\textwidth]{images/nn}
    \caption*{Correction through neural network.}
    \end{subfigure}
    \caption{Word segmentation steps}
    \label{fig:char_segm}
\end{figure*}

@@

\caption{The first element of a possible list of trees for the word 'Yes' with branching factor 2. The characters have the following probabilities: $P(Y)=0.9, P(T)=0.1, P(e)=0.8, P(l)=0.2, P(s)=0.6, P(5)=0.4$. Other characters have probabilities which are neglible.}
